---
title: "ReporterScore"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ReporterScore}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

```{r setup}
library(ReporterScore)
```


# ReporterScore

Generalized Reporter Score-based Enrichment Analysis for Omics Data

## Citation

To cite ReporterScore in publications use:

C. Peng, Q. Chen, S. Tan, X. Shen, C. Jiang, Generalized Reporter Score-based Enrichment Analysis for Omics Data. bioRxiv [Preprint] (2023). https://doi.org/10.1101/2023.10.13.562235.

Please go to https://github.com/Asa12138/ReporterScore for more details.

## Install

```{r eval=FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("Asa12138/pcutils")
devtools::install_github("Asa12138/ReporterScore")
library(ReporterScore)
```

# Need helps?
If you have any questions/issues, please visit [github issue](https://github.com/Asa12138/ReporterScore/issues) tracker. 

# Session information

Here is the output of sessionInfo() on the system on which this document was compiled:

```{r}
sessionInfo()
```

# Reference

1.  Patil, K. R.
    & Nielsen, J. Uncovering transcriptional regulation of metabolism by using metabolic network topology.
    Proc Natl Acad Sci U S A 102, 2685--2689 (2005).

2.  L. Liu, R. Zhu, D. Wu, Misuse of reporter score in microbial enrichment analysis. iMeta. 2, e95 (2023).

3.  <https://github.com/wangpeng407/ReporterScore>
